Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-03 papers/actus2021/article.tex
Tidying up: some formatting of identifiers in math mode; spellings.

\keywords{Cardano \and ACTUS \and blockchain \and finance \and Marlowe \and Haskell} 
\end{abstract}

@@

In the context of ACTUS and other event-based frameworks, there is
one more factor influencing interest rates thrrough scaling:

\noindent 
\begin{equation}
interestPayment=interestScalingFactor*interstRate*notional
\end{equation}

@@

\noindent 
\begin{equation}
payoff_{i}=POF(state_{i})
\end{equation}

@@

\noindent 
\begin{equation}
riskfactor_{i}{}_{t}=O_{rf}(i,t)
\end{equation}

@@

\section{Building executable specification of ACTUS}

@@

where $receiveData$ - is asking an oracle for Marlowe Choice if needed,
$calculatePayoff$ - calculates payoff formula. For fixed-rate contracts
this is optimised into a precalculated constant. $processPayoff$
- awaits Deposit of payoff amount from a party: if deposit is transferred
it redirects the funds to a counterparty - otherwise it transfers
the collateral to a counterparty and closes the contract. The chain
is generated from the fixed (known in advance) schedule of events
using $SCHED()$function from ACTUS.

@@

\noindent 
\begin{equation}
\forall ct\forall rf.getCashFlows("haskell",ct,rf)\equiv getCashFlows("java",ct,rf)
\end{equation}

Where $ct$ represnts contract terms, $rf$ is risk factor model and
$getCashFlows()$ returns a set of $(date,payoff)$ tuples.

>>>>

\keywords{ACTUS \and blockchain \and Cardano \and finance \and Haskell \and Marlowe} 
\end{abstract}

@@

In the context of ACTUS and other event-based frameworks, there is
one more factor influencing interest rates thorough scaling:

\noindent 
\begin{equation}
interestPayment=interestScalingFactor*interestRate*notional
\end{equation}

@@

\noindent 
\begin{equation}
\mbox{\emph{payoff}}_{i}=POF(state_{i})
\end{equation}

@@

\noindent 
\begin{equation}
\mbox{\emph{riskfactor}}_{i}{}_{t}=O_{rf}(i,t)
\end{equation}

@@

\section{Building an executable specification of ACTUS}

@@

where $receiveData$ - is asking an oracle for Marlowe Choice if needed,
$calculatePayoff$ - calculates payoff formula. For fixed-rate contracts
this is optimised into a pre-calculated constant. $processPayoff$
- awaits Deposit of payoff amount from a party: if deposit is transferred
it redirects the funds to a counterparty - otherwise it transfers
the collateral to a counterparty and closes the contract. The chain
is generated from the fixed (known in advance) schedule of events
using $SCHED()$function from ACTUS.

@@

\smallskip
\noindent 
\begin{equation}
\forall ct\forall rf.getCashFlows("haskell",ct,rf)\equiv getCashFlows("java",ct,rf)
\end{equation}

Where $ct$ represents contract terms, $rf$ is risk factor model and
$getCashFlows()$ returns a set of $(date,payoff)$ tuples.
